TITLE

### 2021-02-17 outputs/paper/data_simulation.Rmd
add set seed

---
title: "Simulating data for the Ontario restaurant closures experiment"
author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
subtitle: "SUBTITLE"
abstract: "This document explains how data for the Ontario restaurant closures experiment was simulated, including the research that was used for parameterization and the methods used to randomize data."
thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
bibliography: references.bib
---

@@

# count the numbers for treat, control, and total
num_treat <- first(count(data %>%
                           filter(group == "treatment")))

num_control <- first(count(data %>% 
                             filter(group == "control")))

num_total <- first(count(data))

@@

## Survey 1
```{r}
survey_1 <- survey_1 %>%
```

@@

```{r}
survey_2 <- survey_2 %>%

@@

@@

# Survey 2
```{r}
set.seed(24)
survey_2 <- bind_rows(
  survey_2 %>%
    filter(group == "treatment") %>%
    mutate(shutdown = sample(c("none", "temporary", "permanent"), 
                                                            size = num_treat, 
                                                            prob = c(0.558, 0.432, 0.01),
                                                            replace = TRUE))
  ,
  survey_2 %>%
    filter(group == "control") %>%
    mutate(shutdown = sample(c("none", "temporary", "permanent"), 
                                                          size = num_control, 
                                                          prob = c(.99, 0.005, 0.005),
                                                          replace = TRUE))
) %>%
  arrange(ID)

@@

# Revenue
From https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3310022201&pickMembers%5B0%5D=2.1&pickMembers%5B1%5D=3.423
25,836 employers

@@

## Survey 1
```{r}
set.seed(24)
survey_1 <- survey_1 %>%
  mutate(revenue = 41975 * rf(num_total,10,5))
```

@@

####################### TODO: account for minority owned businesses

## Survey 2
```{r}
survey_2 <- survey_2 %>%
  mutate(revenue = 41975 * rf(num_total,10,5))

@@

survey_2 <-
  bind_rows(
    survey_2 %>%
      filter(minority == "yes" & group == "treatment") %>%
      mutate(revenue = 0.9 * revenue)
    ,
    survey_2 %>%
      filter(minority == "no" & group == "treatment")
    ,
    survey_2 %>%
      filter(group == "control")
  )

>>>>

---
title: "Data for the Ontario Restaurant Closures Experiment"
author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
subtitle: "Simulation Methods and Parameterization Research"
abstract: "This document explains how data for the Ontario restaurant closures experiment was simulated, including the research that was used for parameterization and the methods used to randomize data."
thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
bibliography: references.bib
---

@@

# count the numbers for treat, control, and total
num_treat <- first(count(survey_1 %>%
                           filter(group == "treatment")))

num_control <- first(count(survey_1 %>% 
                             filter(group == "control")))

num_total <- first(count(survey_1))

@@

https://www.ic.gc.ca/eic/site/061.nsf/eng/h_03115.html
0.5% are owned by persons with disabilities

## Survey 1
```{r}
set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(disability = sample(c("yes", "no"),
                             size = num_total,
                             prob = c(0.005, .995),
                             replace = TRUE))

survey_1 <- survey_1 %>%

@@

```{r}
set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(disability = sample(c("yes", "no"),
                             size = num_total,
                             prob = c(0.005, .995),
                             replace = TRUE))

survey_2 <- survey_2 %>%
```

@@

# Survey 2

@@

```{r}
set.seed(19893)
survey_2 <- bind_rows(
  survey_2 %>%
    filter(group == "treatment") %>%
    mutate(shutdown = sample(c("none", "temporary", "permanent"), 
                                                            size = num_treat, 
                                                            prob = c(0.558, 0.432, 0.01),
                                                            replace = TRUE))
  ,
  survey_2 %>%
    filter(group == "control") %>%
    mutate(shutdown = sample(c("none", "temporary", "permanent"), 
                                                          size = num_control, 
                                                          prob = c(.99, 0.005, 0.005),
                                                          replace = TRUE))
) %>%
  arrange(ID)

@@

# Revenue

## Survey 1

From https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3310022201&pickMembers%5B0%5D=2.1&pickMembers%5B1%5D=3.423
25,836 employers

@@

```{r}
set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(revenue = 41975 * rf(num_total,10,5))
```

@@

https://www150.statcan.gc.ca/t1/tbl1/en/cv.action?pid=3310028101
all business had a median decrease of about 15%
minority owned businesses had a median decrease of about 25%.
Decrease of about 12%.

```{r}
set.seed(19894)
survey_2 <- survey_2 %>%
  mutate(revenue = 41975 * rf(num_total,10,5))

@@

survey_2 <-
  bind_rows(
    survey_2 %>%
      filter(minority == "yes" & group == "treatment") %>%
      mutate(revenue = 0.88 * revenue)
    ,
    survey_2 %>%
      filter(minority == "no" & group == "treatment")
    ,
    survey_2 %>%
      filter(group == "control")
  )

### 2021-02-17 outputs/paper/paper.Rmd
rewriting sampling frame and simulation frame to ensure anonymity

@@

@@

### FINDING ONE

### FINDING TWO

### FINDING THREE

>>>>

# NOTE: scripts 01_scrape_health_depts and 02_sampling_frame, 
# and markdown file data_simulation must have been run already

@@

```{r}
treatment_control_groups
```

```{r}
all_units_data
```

```{r}
table_for_surveys
```

```{r}

@@

### FINDING ONE
 Closures had a negative impact

### FINDING TWO
Closures had a stronger negative impact on dine-in only restaurants

### FINDING THREE
CLosures had a stronger negative impact on POC-owned
